Limited information strategies for a topological proximal game

### 2015-05-15 phd/talks-and-presentations/2015-05-13-topological-proximal-game.tex
final draft - add pauses

\begin{frame}
  Our goal is to obtain a purely topological characterization of the
  proximal properties.

@@

  As it turns out, the union of all uniformities inducing a topology is
  itself a uniformity inducing that topology, called the
  \term{fine} or \term{universal uniformity}.
  Furthermore, $\pl D\win\bellAbsConGame{X}$
  if and only if $\pl D$ is required to choose from the universal uniformity.

@@

  This reduces our goal to characterizing the universal entourages.
\end{frame}

@@

  So we topologize Bell's game by simply calling the open symmetric
  neighborhoods of the diagonal with the above property ``entourages'',
  and discard the need to consider a specific uniform structure.
\end{frame}

@@

  Probable counter-example for generalization:
  $\pl D\notmarkwin\bellAbsConGame{\sum_{\alpha<\omega_1} 2}$?
\end{frame}

@@

  \begin{itemize}
  \item Any metric space satisfies \(\pl O\tactwin\gruConGame{X^2}{\Delta}\),
  but \(\pl D\tactwin\bellAbsConGame{X}\) implies zero-dimensionality for
  compact spaces.
  \end{itemize}
\end{frame}

>>>>

\begin{frame}
  Our goal is to obtain a purely topological characterization of the
  proximal property.

@@

  As it turns out, the union of all uniformities inducing a topology is
  itself a uniformity inducing that topology, called the
  \term{fine} or \term{universal uniformity}.
  Furthermore, the proximal property is agnostic to which uniformity
  is chosen for the space's topology.

@@

  If there's a winning strategy for $\pl D$ given any uniformity for
  the topology on $X$, then
  that strategy also works with the universal uniformity for $X$
  containing it.
  This reduces our goal to characterizing the entourages of the
  universal uniformity.
\end{frame}

@@

  So we topologize Bell's game by simply saying an ``entourage''
  is any open symmetric neighborhood of the diagonal with the above property,
  and discard the need to consider a specific uniform structure.
\end{frame}

@@

  It seems likely that
  $\pl D\notmarkwin\bellAbsConGame{\sum_{\alpha<\omega_1} 2}$,
  but I don't have a proof. Whether
  $\pl D\kmarkwin{2}\bellAbsConGame{\sum_{\alpha<\omega_1} 2}$
  holds is less clear.
\end{frame}

@@

  \begin{itemize}
  \item Any metric space satisfies \(\pl O\tactwin\gruConGame{X^2}{\Delta}\),
  but for compact spaces, \(\pl D\tactwin\bellAbsConGame{X}\) implies
  \(X\) is scattered.
  \end{itemize}
\end{frame}
